Latitudinal gradients in biotic niche breadth vary across ecosystem types.

### 2018-04-17 manuscript/latitudepaper.tex
updated figs, main text.

  Link density (mean number of feeding links per species), generality (mean
  number of prey per species), and vulnerability (mean number of predators per
  species) were strongly and positively correlated ($R^2$=\st{0.891}0.890 for link
  density and generality, $R^2$\textgreater0.999 for link density and
  vulnerability, and $R^2$=\st{0.890}0.889 for generality and vulnerability). Contrary
  to the expected latitudinal gradient, the best-fit version of
  equation~(\ref{Latfull}) did not include a significant
  effect of latitude on species richness for any ecosystem type. Further, there were no significant
  relationships between link density, generality, or vulnerability with
  latitude for any ecosystem type.
  % [[After correction: $R^2$=0.890 for link density and generality, $R^2$\textgreater0.999 for link density and vulnerability, and $R^2$=0.889 for generality and vulnerability.]]

@@

  Each measure of specialisation increased with increasing
  species richness ($\beta_0$=\st{0.637}0.668, $p$\textless0.001; $\beta_0$=\st{0.553}0.689,
  $p$\textless0.001; and $\beta_0$=\st{0.637}0.668, $p$\textless0.001, respectively;
  Fig.~\ref{props_v_lat}). 
  % [[After correction: ($\beta_0$=0.668, $p$\textless0.001; $\beta_0$=0.689, $p$\textless0.001; and $\beta_0$=0.668, $p$\textless0.001, respectively).]]
  For estuarine, marine, and terrestrial food webs the
  strength of this scaling did not vary with latitude
  (\st{$\beta_{Latitude}$=-0.001, $p$=0.365 for link density;}
  $\beta_{Latitude}$=\st{-0.001}-0.002, $p$=\st{0.535}0.101 for generality; 
  latitude was not retained in the best-fit models for link density or vulnerability \st{and
  $\beta_{Latitude}$=-0.001, $p$=0.366 for vulnerability}; Fig.~\ref{S}). 
  % [[After correction: latitude not included in LS_min or Vul_min. $\beta_{Latitude}$=-0.002, $p$=0.101 for generality]]
  \st{In lake food webs, however, the scaling of each property was stronger towards
  the poles ($\beta_{Latitude:Lake}$=0.004, $p$=0.019;
  $\beta_{Latitude:Lake}$=0.005, $p$=0.004; and
  $\beta_{Latitude:Lake}$=0.004, $p$=0.018, respectively). In stream food
  webs, generality increased more rapidly towards the poles
  ($\beta_{Latitude:Stream}$=0.007, $p$=0.001) while link density and
  vulnerability did not vary with latitude (i.e., the interaction term 
  $\beta_{Latitude:Stream}$ was not retained in the best-fit models).}
  In lake and stream food webs, however, the scaling of generality was stronger
  towards the poles. This change in scaling was significant for streams but not for
  lakes ($\beta_{Latitude:Stream}$=0.008, $p$\textless0.001 and $\beta_{Latitude:Lake}$=0.003, $p$=0.100, respectively).
  % [[After correction: Link density and vulnerability scaled more strongly with species richness in lake food webs ($\beta_{Lake}$=0.057, $p$=0.024 and $\beta_{Lake}$=0.059, $p$=0.020, respectively). Generality scaled significantly more strongly towards the poles in streams and slightly (not significantly) more strongly towards the poles in lake food webs ($\beta_{Latitude:Stream}$=0.008, $p$\textless0.001 and $\beta_{Latitude:Lake}$=0.003, $p$=0.100, respectively). ]]

@@

\begin{figure}[h]
\centerline{\includegraphics*[height=.5\textheight]{Figures/by_TL/scaling_with_S/proportions/S_fitlines_nonts.eps}}
\caption{Scaling relationships for re-scaled link density, generality, and vulnerability 
relative to the species richness of a food web. Link density, generality,
and vulnerability were each re-scaled to remove the effects of latitude and ecosystem
type. As these relationships take the form of power laws, we did this by dividing the food-web
property (e.g. link density) by species richness raised to an exponent including the 
effects of latitude and, where applicable, ecosystem type and the interaction between ecosystem
type and latitude. Note that in all cases estuarine food webs were treated as the baseline 
ecosystem type, but that at most two ecosystem types had interactions between ecosystem type and
latitude retained in the best-fit model (see \emph{Results} for specifics). For each relationship, 
we show the re-scaled values (white circles) as well as the overall scaling relationship using estuarine
ecosystems as a baseline (black line, N=196 food webs). For a figure with the uncorrected values,
see Fig.~\emph{S7}, \emph{Appendix S4}.}
\label{props_v_lat}
\end{figure}

\begin{figure}[h]
\centerline{\includegraphics*[width=.85\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}}
\caption{Changes to the scaling of link density, generality, and vulnerability with species richness across ecosystem
types and over latitude. We show the estimated scaling exponent for species richness (black
line) with its 95\% confidence interval (in grey), based on N=196 empirical food webs.
Latitude is given in degrees from the equator regardless of direction.} \label{S} \end{figure}

>>>>

  Link density (mean number of feeding links per species), generality (mean
  number of prey per species), and vulnerability (mean number of predators per
  species) were strongly and positively correlated ($R^2$=\st{0.891}\textbf{0.890} for link
  density and generality, $R^2$\textgreater0.999 for link density and
  vulnerability, and $R^2$=\st{0.890}\textbf{0.889} for generality and vulnerability). Contrary
  to the expected latitudinal gradient, the best-fit version of
  equation~(\ref{Latfull}) did not include a significant
  effect of latitude on species richness for any ecosystem type. Further, there were no significant
  relationships between link density, generality, or vulnerability with
  latitude for any ecosystem type.
  % [[After correction: $R^2$=0.890 for link density and generality, $R^2$\textgreater0.999 for link density and vulnerability, and $R^2$=0.889 for generality and vulnerability.]]

@@

  Each measure of specialisation increased with increasing
  species richness ($\beta_0$=\st{0.637}\textbf{0.668}, $p$\textless0.001; $\beta_0$=\st{0.553}\textbf{0.689},
  $p$\textless0.001; and $\beta_0$=\st{0.637}\textbf{0.668}, $p$\textless0.001, respectively;
  Fig.~\ref{props_v_lat}). 
  % [[After correction: ($\beta_0$=0.668, $p$\textless0.001; $\beta_0$=0.689, $p$\textless0.001; and $\beta_0$=0.668, $p$\textless0.001, respectively).]]
  For estuarine, marine, and terrestrial food webs the
  strength of this scaling did not vary with latitude
  (\st{$\beta_{Latitude}$=-0.001, $p$=0.365 for link density;}
  $\beta_{Latitude}$=\st{-0.001}\textbf{-0.002}, $p$=\st{0.535}\textbf{0.101 for generality; 
  latitude was not retained in the best-fit models for link density or vulnerability}\st{and
  $\beta_{Latitude}$=-0.001, $p$=0.366 for vulnerability}; Fig.~\ref{S}). 
  % [[After correction: latitude not included in LS_min or Vul_min. $\beta_{Latitude}$=-0.002, $p$=0.101 for generality]]
  \st{In lake food webs, however, the scaling of each property was stronger towards
  the poles ($\beta_{Latitude:Lake}$=0.004, $p$=0.019;
  $\beta_{Latitude:Lake}$=0.005, $p$=0.004; and
  $\beta_{Latitude:Lake}$=0.004, $p$=0.018, respectively). In stream food
  webs, generality increased more rapidly towards the poles
  ($\beta_{Latitude:Stream}$=0.007, $p$=0.001) while link density and
  vulnerability did not vary with latitude (i.e., the interaction term 
  $\beta_{Latitude:Stream}$ was not retained in the best-fit models).}
  In \textbf{lake and} stream food webs, however, the scaling of generality was stronger
  towards the poles. This change in scaling was significant for streams but not for
  lakes ($\beta_{Latitude:Stream}$=0.008, $p$\textless0.001\textbf{ and $\beta_{Latitude:Lake}$=0.003, $p$=0.100, respectively}).
  % [[After correction: Link density and vulnerability scaled more strongly with species richness in lake food webs ($\beta_{Lake}$=0.057, $p$=0.024 and $\beta_{Lake}$=0.059, $p$=0.020, respectively). Generality scaled significantly more strongly towards the poles in streams and slightly (not significantly) more strongly towards the poles in lake food webs ($\beta_{Latitude:Stream}$=0.008, $p$\textless0.001 and $\beta_{Latitude:Lake}$=0.003, $p$=0.100, respectively). ]]

@@

\begin{figure}[h]
\centerline{\includegraphics*[height=.5\textheight]{Figures/by_TL/scaling_with_S/proportions/S_fitlines_nonts_new.eps}}
\caption{Scaling relationships for re-scaled link density, generality, and vulnerability 
relative to the species richness of a food web. Link density, generality,
and vulnerability were each re-scaled to remove the effects of latitude and ecosystem
type. As these relationships take the form of power laws, we did this by dividing the food-web
property (e.g. link density) by species richness raised to an exponent including the 
effects of latitude and, where applicable, ecosystem type and the interaction between ecosystem
type and latitude. Note that in all cases estuarine food webs were treated as the baseline 
ecosystem type, but that at most two ecosystem types had interactions between ecosystem type and
latitude retained in the best-fit model (see \emph{Results} for specifics). For each relationship, 
we show the re-scaled values (white circles) as well as the overall scaling relationship using estuarine
ecosystems as a baseline (black line, N=196 food webs). For a figure with the uncorrected values,
see Fig.~\emph{S7}, \emph{Appendix S4}.}
\label{props_v_lat}
\end{figure}

\begin{figure}[h]
%\centerline{\includegraphics*[width=.85\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}}
\centerline{\includegraphics*[width=.85\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_non_TS_updated.eps}}
\caption{Changes to the scaling of link density, generality, and vulnerability with species richness across ecosystem
types and over latitude. We show the estimated scaling exponent for species richness (black
line) with its 95\% confidence interval (in grey), based on N=196 empirical food webs.
Latitude is given in degrees from the equator regardless of direction.} \label{S} \end{figure}
